---
title: "Results of a Practice Stroop Trial"
date: "2023-11-14"
---

### Results of a Stroop Trial

#### Two Levels Focus on Words, Ignore Words

##### Observations

##### THere is a greater difference in the reaction time during congruent and incongruent trials on the ignore words condition. There was a smaller difference in reaction time during congruent and incongruent trials on the focus condition

##### The congruent reaction time for focus condition was longer than the reaction time for ignore condition

##### It seems I was not able to completely abandon paying more attention on the words during the condition that presented "focus on words" and my trials took a longer time.

```{r, echo=FALSE, message=FALSE, include=FALSE}

library(tidyverse)
library(dplyr)
library(ggthemes)
library(readxl)
library(reshape2)
library(knitr)
library(ggrepel)
library(magrittr)


foo_hw <- read_xlsx("hw_attention_trial.xlsx")

glimpse(foo_hw)

foo_hw$trial_type %<>% factor


foo_hw







```


###### In the following graph stroop effect time is just displayed as a range and does not necessarily correspond to either line graph

```{r  fig.align="center", echo = FALSE,fig.width = 10}




ggplot(data=foo_hw)+
  geom_line(mapping=aes(stroop_effect_time, incongruent,  color="incongruent"))+
 geom_line(mapping=aes(stroop_effect_time , congruent, color="congruent"))+
  scale_y_continuous(n.breaks=15)+
  scale_x_continuous(n.breaks=15)+
     theme(axis.text.x = element_text(angle=90 ,vjust=1, hjust=1))+
            labs(
            x="Range of Stroop Effect Time in milliseconds from Smallest to Largest ",
            y="Congruent Versus Incongruent Trials in Milliseconds",
            title="Differences in Stroop Effect for Congruent versus Incongruent Trials in Focus and Ignore Conditions")+
  theme_light()+
  theme( axis.line = element_line(colour = "lightgreen", 
                      size = 1, linetype = "solid"))

```
